\LARGE \bf Steering a Swarm Using Global Inputs\\ and Swarm Statistics

### 2017-05-05 journalSwarmControl/conclusion.tex
Thanked reviewers

Inspired by the three lessons from swarmcontrol.net, this paper designed controllers and controllability results using only the mean and variance of a particle swarm. 
We developed a hysteresis based controller to regulate the position and variance of a swarm. We designed a controller for object manipulation using policy iteration for path planning, regions for outlier rejection, and potential fields for minimizing moving the object backwards. 
All automatic controllers were implemented using 100 kilobots steered by the direction of a global light source.
These experiments culminated in an object manipulation task in a workspace with obstacles.

>>>>

Inspired by the three lessons from \href{www.swarmcontrol.net}{swarmcontrol.net}, this paper designed controllers and controllability results using only the mean and variance of a particle swarm. 
We developed a hysteresis based controller to regulate the position and variance of a swarm. We designed a controller for object manipulation using policy iteration for path planning, regions for outlier rejection, and potential fields for minimizing moving the object backwards. 
All automatic controllers were implemented using 100 kilobots steered by the direction of a global light source.
These experiments culminated in an object manipulation task in a workspace with obstacles.
